---
title: "人工神經網絡@銀聯強積金 - MPF-ANN in BCT MPF Scheme"
output: 
  header-includes: 
  - \usepackage{xeCJK}
  - \setCJKmainfont{Noto Sans CJK HK}
  - \setmainfont{Noto Sans CJK HK}
  - \setmonofont{Noto Mono}
  pdf_document:
    latex_engine: xelatex
    df_print: paged
    keep_tex: TRUE
    #extra_dependencies: c("fontspec", "ctex")
---
# Portfolio management using Artifical Neural Network (ANN) in BCT MPF
# 銀聯強積金應用人工類神經網絡進行資產調配

## Disclamier of warranties

1. The author (jchan-gi) expressly stated that nothing my repositories and webpages
constitutes any advices or recommendation on investing or allocating assets on any
stock or financial products.    
2. No content in my study have been prepared with respect to specific personal need
and investment objects of individuals. All materials reveal to the public are applicable
to the author (jchan-gi) only.
3. All investors shall obtain kind advices from professional financial consultants before
making any decisions. Professional financial consultants should recommend products 
or decisions that suit your needs and objectives.    
4. The author is not licensed nor professional in the field hence this studies are not 
professional advice and may not be suitable for anyone except myself. 

### Last update: 2019/11/23.


### Changelog (from v8)
### The algorithm have been changed significantly on 2019/08/15.
We removed the VIX condition in our algorithm.   
Changes in condition of hedge are also expected.   
Three major outcomes is targeted in our study:   
1. ~8-10% annualized return    
2. <10% annualized standard deviation (~3% monthly)   
3. >1 sharpe ratio   

### Monthly installment results available from 2019/09/12.   

### Due to extreme volality and manipulated market, the Chinese Tracker fund (col = 4) have been manually excluded from calculation with effect from 2019/09/12.  

### The raw data feed into the neural network have modified into timestep format on 2019/11/22.   

## WARNING: Please understand nature of ANN in this section before applying MPF-ANN:  
## 警告：在應用MPF-ANN之前，請先於此節了解人工類神經網絡的特性
This script relies on artifical neural network (ANN) model for MPF fund allocation.   
ANN is stochastic in nature. In default mode, It produces different results based on the pseudo-random seed (system time).   
The mean of 30 portfolios with defined seed have been generated in order to generate replicable result.
An trustworthy statistics, deflated sharpe ratio, is used for estimating overfitting of the model. The result of deflated sharpe ration reflectes the percentage of a model have position return due to less overfitting.      
The model also perform walk-forward validation. 
A model will be created for exactly next re-balance only based on most updated data for that moment.

There is no other validation or assessment on the data.     
Two validation shall give reasonable assessment on the return estimation.   
However, please be reminded that backtesting is no way to be accurate in predicting future performance.     

MPF-ANN根據人工類神經網絡的預測回報作強積金基金調動。    
然而，人工類神經網絡是一隨機過程。在預設的情況下，人工類神經網絡會根據系統時間設定種子，因此每次的執行結果也不盡相同。   
為提高結果的可複製性，本程式以隨機方式抽取了30個種子以重複生成模型及計算平均值。   
平均值模型將用以計算學術論文提出的過擬合夏普比率(意譯自deflated sharpe ratio) 來測定人工類神經網絡模型過擬合(overfitting)的程度。過擬合夏普比率數值代表了模型因沒有過度擬合而將有正回報的機率。  
此外，此模式亦使用了前移式回測(walk-forward validation)。
每次資產調配都會基於擁有最新資料(當時而言)而建立的人工類神經網結模型。

此模型只建基於上述兩項的檢測。   
上述的檢測應可視為MPF-ANN所計算的回測結果可靠程度的參考指標。   
然而，請切記過往表現不代表將來表現。    

### Background Introduction
### 背景簡介    
Mandatory Provident Fund (MPF) is one of the legal pensions in Hongkong.  
All Employers and some employees are required to pay at least 5% of monthly salary to MPF services provider.  
MPF providers are required to provide approved funds for employees to invest, 
while the team could earn management fees.  

However, the average annualized return of MPF is 3.1% only in from 2000-2016 (Mandatory Provident Fund Schemes Authority, 2016).  
Most Hongkong employees feels they are forced to give their salary to fund manager.  
Indeed, the reasons of low return may due to inactive management by employees.  
In this example, we will explore artifical neural network to rise the annualized return.  

在香港，強積性公積金(強積金, Mandatory Provident Fund, MPF)是其中一種法定退休金。   
僱主及部份僱員須扣除5%薪金供強積金營運商。
強積金營運商將每月收取管理費，並提供認可基金供僱員作投資儲蓄。


### BCT MPF Portfolio Generation using Artifical Neural Network (ANN) Relative Strength Index   

Artifical Neural Network is a stochastic black-box model. It receives input and output the result by passing weighted values in neurons.   
Formal definition could be searched on internet.   
To support our application, we will uses Relative Strength Index (RSI) (customized period) to refine our prices.   
RSI shows whether a stock/fund overbuy (or oversell) hence overpriced (or underpriced).  

In our example, we directly uses Long-Short Term Memory to train and predict the future price of MPF constitute fund prices.  
The fund would be finalized by applying penalty based on the result of RSI and VIX.

### When to manage?

In this example, we are going to collect daily price for all MPF fund in last day of a month.  
Then, we are going to convert or reallocate the assets at the same time.  
Notice that it is impossible since MPF price are uploaded 1 business day, also reallocation need at lest 2 business day to achieve.  

### Results

Using Top 2 Performers in LSTM ANN (Lastest rebalance date: 2019/07/31)  

Annualized Return: ~11.88%   
Mean Annual Return: ~11.47%      
Annualized Standard Deviation: ~9.49% (StdDev(monthly return) * sqrt(12))   
Sharpe Ratio (Mean Annual Return): 11.47%/9.49% = 1.2091    
Sortino Ratio: 0.8054 (MAR = 0%)  
Expected Shortfall: 4.46% loss (0% Risk-free rate, 95% C.I.)   
Deflated Sharpe Ratio (p-value): >99.9999% (rounded to 1)     

Monthly installment:    
Total contribution: 337500    
Latest asset value: 1048491    
Mean annual return: 10.14%      
Internal Rate of Return (IRR): 10.41%    
Annualized Standard Deviation: 9.46%    
Sharpe Ratio: 1.0722          
Sortino Ratio: 0.7324 (MAR = 0%)    
Expected Shortfall: 4.53% loss (0% Risk-free rate, 95% C.I.)     


## Recommended Parameters

| Variable     | Val.     | Explanation                               |
| ------------ | -------- | ----------------------------------------- |
| top          | 2        | Top n Performer                           |
| RSI_Overbuy  | 0.85     | RSI indicator (%)                         |    
| RSI_Period   | 18       | MA period for RSI (months)                |
| Min_NMMA     | 0.001    | Minimum Monthly Return to be consider     |   
| lr           | 0.0013   | Learning rate of ANN                      |      
| epoch        | 36       | Epoch in ANN                              |     


## Detailed Workflow

### Package Preparation

```{r linewidth=159, wrap-hook, results="hide", eval=FALSE, echo=FALSE}
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

1. Install necessary packages

```{r linewidth=159, warning=FALSE, results="hide", eval=FALSE}
r = getOption("repos")
r["CRAN"] = "https://mran.revolutionanalytics.com/snapshot/2019-11-01"
options(repos = r)
install.packages("zoo")
install.packages("xts")
install.packages("fBasics")
install.packages("quantmod")
install.packages("PerformanceAnalytics")


```

2. Now load necessary packages.
```{r linewidth=159, warning=FALSE, results="hide"}

library("dplyr")
library("zoo")
library("xts")
library("fBasics")
library("quantmod")
library("PerformanceAnalytics")
library("feather")

library("doParallel")


```

### Load Prices and Calculate Return

0. Parameters
```{r linewidth=159, warning=FALSE}
top <- 2
RSI_Overbuy <- 0.85
RSI_Period <- 18 
Min_NMMA <- 1e-6
```

1. Load the price into zoo format
```{r linewidth=159, warning=FALSE}
setwd("~")
MPF.BCT <-
  as.xts(
    read.zoo(
      "MPF/BCT/BCT.csv",
      format = "%Y/%m/%d",
      header = TRUE,
      read = read.csv,
      na.strings = "0"
    )
  )
daily <- index(MPF.BCT)
monthly.old <- index(MPF.BCT.returns)
MPF.BCT.w.all.backup <- MPF.BCT.w.all

```



2. Calculate Relative Strength Index (RSI)
```{r linewidth=159, include=FALSE, results=FALSE}
MPF.BCT.RSI <- na.fill(apply(MPF.BCT, 2, function(x) RSI(x, n=21*RSI_Period)),0)
MPF.BCT.RSI <- as.xts(MPF.BCT.RSI, order.by = daily)
```


3. Calculate Returns
```{r linewidth=159, warning=FALSE}

MPF.BCT.AE <- monthlyReturn(as.xts(MPF.BCT$AE), type = "log")
MPF.BCT.CA <- monthlyReturn(as.xts(MPF.BCT$CA), type = "log")
MPF.BCT.CEHK <- monthlyReturn(as.xts(MPF.BCT$CEHK), type = "log")
MPF.BCT.CT <- monthlyReturn(as.xts(MPF.BCT$CT), type = "log")
MPF.BCT.EU <- monthlyReturn(as.xts(MPF.BCT$EU), type = "log")
MPF.BCT.E3 <- monthlyReturn(as.xts(MPF.BCT$E30), type = "log")
MPF.BCT.E5 <- monthlyReturn(as.xts(MPF.BCT$E50), type = "log")
MPF.BCT.E7 <- monthlyReturn(as.xts(MPF.BCT$E70), type = "log")
MPF.BCT.E9 <- monthlyReturn(as.xts(MPF.BCT$E90), type = "log")
MPF.BCT.FM <- monthlyReturn(as.xts(MPF.BCT$FM), type = "log")

MPF.BCT.GB <- monthlyReturn(as.xts(MPF.BCT$GB), type = "log")
MPF.BCT.GE <- monthlyReturn(as.xts(MPF.BCT$GE), type = "log")
MPF.BCT.GT <- monthlyReturn(as.xts(MPF.BCT$GT), type = "log")
MPF.BCT.HKB <- monthlyReturn(as.xts(MPF.BCT$HKB), type = "log")
MPF.BCT.HSIT <- monthlyReturn(as.xts(MPF.BCT$HSIT), type = "log")
MPF.BCT.MPFC <- monthlyReturn(as.xts(MPF.BCT$MPFC), type = "log")
MPF.BCT.RMBB <- monthlyReturn(as.xts(MPF.BCT$RMBB), type = "log")
MPF.BCT.SFP <- monthlyReturn(as.xts(MPF.BCT$SFP), type = "log")
MPF.BCT.SE40 <- monthlyReturn(as.xts(MPF.BCT$SE2040), type = "log")


MPF.BCT.returns <-
  merge(
    MPF.BCT.AE,
    MPF.BCT.CA,
    MPF.BCT.CEHK,
    MPF.BCT.CT,
    MPF.BCT.EU,
    MPF.BCT.E3,
    MPF.BCT.E5,
    MPF.BCT.E7,
    MPF.BCT.E9,
    MPF.BCT.FM,
    MPF.BCT.GB,
    MPF.BCT.GE,
    MPF.BCT.GT,
    MPF.BCT.HKB,
    MPF.BCT.HSIT,
    MPF.BCT.MPFC,
    MPF.BCT.RMBB,
    MPF.BCT.SFP,
    MPF.BCT.SE40
  )

MPF.BCT.original.cost <-
  c(
    0.0182,
    0.0085,
    0.0166,
    0.0115,
    0.0165,
    0.0163,
    0.0163,
    0.0162,
    0.0152,
    0.0136,
    0.0150,
    0.0167,
    0.0100,
    0.0112,
    0.0084,
    0.0094,
    0.0126,
    0.0082,
    0.0150
  ) / 12
MPF.BCT.cs.cost <-
  c(
    0.0069,
    0.0062,
    0.0069,
    0.0060,
    0.0069,
    0.0062,
    0.0062,
    0.0062,
    0.0062,
    0.0062,
    0.0055,
    0.0069,
    0.0060,
    0.0055,
    0.0050,
    0.0040,
    0.0055,
    0.0062,
    0.0062
  ) / 12

for (col in 1:length(MPF.BCT.returns[1, ])) {
  MPF.BCT.returns[, col] <-
    MPF.BCT.returns[, col] - MPF.BCT.cs.cost[col] + MPF.BCT.original.cost[col]
}


monthly <- index(MPF.BCT.returns)
#monthly <- length(monthly)
MPF.BCT.colnames <- 
  c(
    "MPF.BCT.AE",
    "MPF.BCT.CA",
    "MPF.BCT.CEHK",
    "MPF.BCT.CT",
    "MPF.BCT.EU",
    "MPF.BCT.E3",
    "MPF.BCT.E5",
    "MPF.BCT.E7",
    "MPF.BCT.E9",
    "MPF.BCT.FM",
    "MPF.BCT.GB",
    "MPF.BCT.GE",
    "MPF.BCT.GT",
    "MPF.BCT.HKB",
    "MPF.BCT.HSIT",
    "MPF.BCT.MPFC",
    "MPF.BCT.RMBB",
    "MPF.BCT.SFP",
    "MPF.BCT.SE2040"
  )

colnames(MPF.BCT.returns) <- MPF.BCT.colnames
  
rm(
  MPF.BCT.AE,
  MPF.BCT.CA,
  MPF.BCT.CEHK,
  MPF.BCT.CT,
  MPF.BCT.EU,
  MPF.BCT.E3,
  MPF.BCT.E5,
  MPF.BCT.E7,
  MPF.BCT.E9,
  MPF.BCT.FM,
  MPF.BCT.GB,
  MPF.BCT.GE,
  MPF.BCT.GT,
  MPF.BCT.HKB,
  MPF.BCT.HSIT,
  MPF.BCT.MPFC,
  MPF.BCT.RMBB,
  MPF.BCT.SFP,
  MPF.BCT.SE40
)



```

### Calculate average RSI of the month, and then adjustment factor
Adjustment factor = 1 - ECDF of RSI of that month
New weight = old weight * (0.05 + adjustment factor)
Finally normalize it to sum(row) = 1

```{r linewidth=159, warning=FALSE}
MPF.BCT.RSI.month <-
  as.xts(do.call(rbind, lapply(split(as.xts(MPF.BCT.RSI), "months"), function(x)
    colAvgs(x))), order.by = monthly)
MPF.BCT.RSI.p <- MPF.BCT.returns
MPF.BCT.RSI.p[, ] <- 0
for (col in 1:length(MPF.BCT.RSI.month[1, ])) {
  if (col != 16) {
    for (row in 1:length(MPF.BCT.RSI.month[, col])) {
      percentile <- ecdf(as.numeric(MPF.BCT.RSI.month[1:row, col]))
      if (percentile(MPF.BCT.RSI.month[row, col]) >= (RSI_Overbuy - ((length(1:row) ^
                                                                      (1 / 3)) / (length(1:row) ^ (1 / 2))))) {
        MPF.BCT.RSI.p[row, col] <- 0.4
      } else {
        MPF.BCT.RSI.p[row, col] <-
          1.4 - (percentile(MPF.BCT.RSI.month[row, col]) ^ 2)
      }
    }
    
  } else {
    MPF.BCT.RSI.p[, col] <- 1
  }
}
MPF.BCT.RSI.sum <-
  as.xts(rowSums(MPF.BCT.RSI.p), order.by = monthly)
for (row in 1:length(MPF.BCT.RSI.p[, col])) {
  MPF.BCT.RSI.p[row, ] = apply(MPF.BCT.RSI.p[row, ], 2, function(x)
    (x / MPF.BCT.RSI.sum[row, 1]) ^ (0.25))
}
MPF.BCT.RSI.sum <-
  as.xts(rowSums(MPF.BCT.RSI.p), order.by = monthly)



```

### load python data
```{r warning=FALSE, results="hide"}

MPF.BCT.w.all <- array(MPF.BCT.returns,
                        c(length(MPF.BCT.returns[,1]),length(MPF.BCT.returns[1,]),30))
MPF.BCT.w.all[,,] <- 0

max_return <- c()
min_return <- c()

for (col in 1:length(MPF.BCT.returns[1,])) {
  max_return[col] <- max(na.omit(MPF.BCT.returns[,col]))
  min_return[col] <- min(na.omit(MPF.BCT.returns[,col]))
}

for (i in 1:30) {
  MPF.BCT.w.all[,,i] <- data.matrix(as.data.frame(read_feather(paste("/home/jchan/MPF-ANN/temp/mpf_bct_tcn_w_all.feather",i, sep=""))), rownames.force = NA)
}
```


### Calculate the weight according to predicted return
```{r linewidth=159, warning=FALSE, eval=FALSE}
MPF.BCT.w <- MPF.BCT.returns
MPF.BCT.w[, ] <- 0

MPF.BCT.w <- rowAvgs(MPF.BCT.w.all, dims = 2)
MPF.BCT.w[MPF.BCT.w == 0] <- NA
for (col in 1:length(MPF.BCT.w[1, ])) {
  MPF.BCT.w[, col] <-
    ((MPF.BCT.w[, col] + 1) / 2 * (max_return[col] - min_return[col]) + min_return[col])
}



MPF.portf.weight <- MPF.BCT.returns
MPF.portf.weight[,] <- NA
MPF.portf.weight.all <- MPF.BCT.returns
MPF.portf.weight.all[, ] <- NA
colnames(MPF.portf.weight) <-
  c(
    "MPF.BCT.AE",
    "MPF.BCT.CA",
    "MPF.BCT.CEHK",
    "MPF.BCT.CT",
    "MPF.BCT.EU",
    "MPF.BCT.E3",
    "MPF.BCT.E5",
    "MPF.BCT.E7",
    "MPF.BCT.E9",
    "MPF.BCT.FM",
    "MPF.BCT.GB",
    "MPF.BCT.GE",
    "MPF.BCT.GT",
    "MPF.BCT.HKB",
    "MPF.BCT.HSIT",
    "MPF.BCT.MPFC",
    "MPF.BCT.RMBB",
    "MPF.BCT.SFP",
    "MPF.BCT.SFP",
    "MPF.BCT.SE2040"
  )

MPF.BCT.stock.return <-
  as.xts(rowSums(MPF.BCT.RSI.month), order.by = monthly)
MPF.BCT.stock.return[] <- NA
MPF.portf.return <-
  as.xts(rowSums(MPF.BCT.RSI.month), order.by = monthly)
MPF.portf.return[] <- NA


MPF.BCT.returns.mat <- as.matrix(MPF.BCT.returns)

MPF.BCT.p <- as.matrix(MPF.BCT.returns)
MPF.BCT.p[,] <- 0
SR.all <- c()


hedge <- FALSE
up <- TRUE
round_percent <- function(x) {
  x <- x * 100
  result <- floor(x)    # Find integer bits
  remain <- x - result
  rsum <- sum(result)   # Find out how much we are missing
  i <- 1
  if (rsum < 100) {
    o <- order(remain, decreasing = TRUE)
    while (rsum < 100) {
      if (i > length(remain))
        i <- 1
      idx <- o[i]
      if (result[idx] == 0) {
        i <- i + 1
        next
      }
      result[idx] <- result[idx] + 1
      rsum <- sum(result)
      i <- i + 1
    }
  }
  result <- result / 100
  return(result)
}


for (row in 1:length(MPF.BCT.w[, 1])) {
  MPF.BCT.stock.mean <- 0
  i <- 0
  
  for (col in 1:length(MPF.BCT.w[1,])) {
    MPF.BCT.w[row, col] <-
      na.fill((MPF.BCT.w[row, col]) * MPF.BCT.RSI.p[row, col], 0)
    
    if (col != 2 &&
        col != 6 &&
        col != 7 &&
        col != 11 && col != 14 && col != 16 && col != 17 && col != 18) {
      if (!is.na(MPF.BCT.returns.mat[row, col]) &&
          MPF.BCT.returns.mat[row, col] != 0) {
        MPF.BCT.stock.mean <-
          MPF.BCT.stock.mean + MPF.BCT.returns.mat[row, col]
        i <- i + 1
      }
      
      if (col == 3 || col == 4 || MPF.BCT.w[row, col] < 1e-6) {
        MPF.BCT.w[row, col] <- 0
      }
    } else {
      if (MPF.BCT.w[row, col] < 0) {
        MPF.BCT.w[row, col] <- 0
      }
    }
  }
  
  MPF.BCT.stock.return[row] <- MPF.BCT.stock.mean / i
  
  # Retain two most increasing fund
  last <- length(MPF.BCT.w[1,]) - top
  order <- order(MPF.BCT.w[row,])
  for (col in order[1:last]) {
    MPF.BCT.w[row, col] <- 0
  }
  
  
  
  if (row > 12 &&
      MPF.BCT.stock.return[row] >
      quantile(na.omit(MPF.BCT.stock.return), c(.35))  &&
      MPF.BCT.stock.return[(row - 3)] >
      quantile(na.omit(MPF.BCT.stock.return), c(.45))) {
    up <- FALSE
  }
  
  if (row > 12 && hedge &&
      MPF.BCT.stock.return[(row)]>
      quantile(na.omit(MPF.BCT.stock.return), c(.55))  &&
      MPF.BCT.stock.return[(row - 3)] >
      quantile(na.omit(MPF.BCT.stock.return), c(.35))) {
    hedge <- FALSE
    up <- TRUE
  }
  
  if (row > 12 &&  (MPF.BCT.stock.return[row] < 0 &&
                   MPF.BCT.stock.return[row - 1] >
                   quantile(na.omit(MPF.BCT.stock.return), c(.75)))) {
    hedge <- TRUE
  }
  
  MPF.BCT.w.sum <- sum(MPF.BCT.w[row,])
  
  
  if (row <= 15 || MPF.BCT.w.sum == MPF.BCT.w[row, 16] ||
      MPF.BCT.w.sum < 1e-6 || hedge == TRUE) {
    if (row >= 24) {
      MPF.BCT.p[row, 11] <- 0.35
      MPF.BCT.p[row, 16] <- 0.65
    } else {
      MPF.BCT.p[row, 16] <- 1
    }
  } else if (length(which(MPF.BCT.w[row,] != 0)) == 1 ||
             min(MPF.BCT.stock.return[(row - 3):row]) < -0.065){
    if (row >= 24) {
      MPF.BCT.p[row,] <- MPF.BCT.w[row,] / MPF.BCT.w.sum / 3
      MPF.BCT.p[row, 11] <- MPF.BCT.p[row, 11] + 0.45
      MPF.BCT.p[row, 16] <- MPF.BCT.p[row, 16] + 0.22
    } else {
      MPF.BCT.p[row,] <- MPF.BCT.w[row,] / MPF.BCT.w.sum / 3
      MPF.BCT.p[row, 16] <- MPF.BCT.p[row, 16] + 0.67
    }
  } else {
    MPF.BCT.p[row,] <- MPF.BCT.w[row,] / MPF.BCT.w.sum
  }
  
  MPF.portf.weight[row,] <- round_percent(MPF.BCT.p[row,])
  portf.rebal.fm <-
    Return.portfolio(
      MPF.BCT.returns,
      weight = MPF.portf.weight,
      geometric = TRUE,
      rebalance_on = "months"
    )
  MPF.portf.return[row] <-
    tail(na.omit(portf.rebal.fm), 1)
  MPF.portf.drawdown <- Drawdowns(MPF.portf.return,
                                  geometric = TRUE)
  if (tail(na.omit(MPF.portf.drawdown), 1) < -0.065 &&
      up == FALSE) {
    hedge = TRUE
  }
}

for (pass in 1:30)  {
  MPF.BCT.w.i <- MPF.BCT.w
  MPF.BCT.w.i[,] <- MPF.BCT.w.all[, ,pass]
  MPF.BCT.w.i[MPF.BCT.w.i == 0] <- NA
  for (col in 1:length(MPF.BCT.w[1, ])) {
    MPF.BCT.w.i[, col] <-
      ((MPF.BCT.w.i[, col] + 1) / 2 * (max_return[col] - min_return[col]) + min_return[col])
  }
  MPF.BCT.returns.mat <- as.matrix(MPF.BCT.w.all[, , pass])

  for (row in 1:length(MPF.BCT.w.i[, 1])) {
    MPF.BCT.stock.mean <- 0
    i <- 0

    for (col in 1:length(MPF.BCT.w.i[1,])) {
      MPF.BCT.w.i[row, col] <-
        na.fill((MPF.BCT.w.i[row, col]) * MPF.BCT.RSI.p[row, col], 0)

      if (col != 2 &&
          col != 6 &&
          col != 7 &&
          col != 11 && col != 14 && col != 16 && col != 17 && col != 18) {
        if (!is.na(MPF.BCT.returns.mat[row, col]) &&
            MPF.BCT.returns.mat[row, col] != 0) {
          MPF.BCT.stock.mean <-
            MPF.BCT.stock.mean + MPF.BCT.returns.mat[row, col]
          i <- i + 1
        }

        if (col == 3 || col == 4 || MPF.BCT.w.i[row, col] < 1e-6) {
          MPF.BCT.w.i[row, col] <- 0
        }
      } else {
        if (MPF.BCT.w.i[row, col] < 0) {
          MPF.BCT.w.i[row, col] <- 0
        }
      }
    }

    MPF.BCT.stock.return[row] <- MPF.BCT.stock.mean / i

    # Retain two most increasing fund
    last <- length(MPF.BCT.w.i[1,]) - top
    order <- order(MPF.BCT.w.i[row,])
    for (col in order[1:last]) {
      MPF.BCT.w.i[row, col] <- 0
    }

    #print("segment 1")

    if (row > 12 &&
        MPF.BCT.stock.return[row] >
        quantile(na.omit(MPF.BCT.stock.return), c(.35))  &&
        MPF.BCT.stock.return[row - 3] >
        quantile(na.omit(MPF.BCT.stock.return), c(.55))) {
      up <- FALSE
    }

    if (row > 12 && hedge &&
        MPF.BCT.stock.return[row] >
        quantile(na.omit(MPF.BCT.stock.return), c(.55))  &&
        MPF.BCT.stock.return[row - 3] >
        quantile(na.omit(MPF.BCT.stock.return), c(.35))) {
      hedge <- FALSE
      up <- TRUE
    }

    if (row > 12 &&  (MPF.BCT.stock.return[row] < 0 &&
                     MPF.BCT.stock.return[row - 1] >
                     quantile(na.omit(MPF.BCT.stock.return), c(.75)))) {
      hedge <- TRUE
    }

    MPF.BCT.w.sum <- sum(MPF.BCT.w.i[row,])
    MPF.BCT.p[row, ] <- 0

    if (row <= 15 || MPF.BCT.w.sum == MPF.BCT.w.i[row, 16] ||
        MPF.BCT.w.sum < 1e-6 || hedge == TRUE) {
      if (row >= 24) {
        MPF.BCT.p[row, 11] <- 0.35
        MPF.BCT.p[row, 16] <- 0.65
      } else {
        MPF.BCT.p[row, 16] <- 1
      }
    } else if (length(which(MPF.BCT.w.i[row,] != 0)) == 1 ||
               min(MPF.BCT.stock.return[(row - 3):row]) < -0.065) {
      if (row >= 24) {
        MPF.BCT.p[row,] <- MPF.BCT.w.i[row,] / MPF.BCT.w.sum / 3
        MPF.BCT.p[row, 11] <- MPF.BCT.p[row, 11] + 0.45
        MPF.BCT.p[row, 16] <- MPF.BCT.p[row, 16] + 0.22
      } else {
        MPF.BCT.p[row,] <- MPF.BCT.w.i[row,] / MPF.BCT.w.sum / 3
        MPF.BCT.p[row, 16] <- MPF.BCT.p[row, 16] + 0.67
      }
    } else {
      MPF.BCT.p[row,] <- MPF.BCT.w.i[row,] / MPF.BCT.w.sum
    }

    MPF.portf.weight.all[row, ] <-
      round_percent(MPF.BCT.p[row,])

    portf.rebal.i <-
      Return.portfolio(
        MPF.BCT.returns,
        weight = MPF.portf.weight.all,
        geometric = TRUE,
        rebalance_on = "months"
      )

    MPF.portf.return[row] <- tail(na.omit(portf.rebal.fm), 1)
    MPF.portf.drawdown <- Drawdowns(MPF.portf.return,
                                    geometric = TRUE)
    if (row > 12 && tail(na.omit(MPF.portf.drawdown), 1) < -0.065 &&
        up == FALSE) {
      hedge = TRUE
    }
  }
  SR.all[pass] <- Return.annualized(portf.rebal.i, geometric = TRUE) / (StdDev(portf.rebal.i) * sqrt(12))
}
```

### Performance Analysis
```{r linewidth=159, warning=FALSE}
portf.rebal.fm <- Return.portfolio(
  MPF.BCT.returns,
  weight = MPF.portf.weight,
  geometric = TRUE,
  rebalance_on = "months"
)
mean.annual.return <-
  mean(do.call(rbind, lapply(split(portf.rebal.fm, "years"), function(x)
    colMeans(x))) * 12)
charts.PerformanceSummary(
  portf.rebal.fm,
  methods = "ModifiedES",
  geometric = TRUE,
  p = .95,
  main = "BCT MPF Scheme First Contribution Performance"
)
portf.rebal.fm.sharpe <-
  Return.annualized(portf.rebal.fm, geometric = TRUE) / (StdDev(portf.rebal.fm) * sqrt(12))
portf.rebal.fm.mean.sharpe <-
  mean.annual.return / (StdDev(portf.rebal.fm) * sqrt(12))
rownames(portf.rebal.fm.sharpe) <- "Sharpe Ratio (annualized)"
rownames(portf.rebal.fm.mean.sharpe) <-
  "Sharpe Ratio (mean annual return)"
colnames(portf.rebal.fm.mean.sharpe) <- "portfolio.returns"
Return.annualized(portf.rebal.fm, geometric = TRUE)
mean.annual.return
portf.rebal.fm.sharpe
portf.rebal.fm.mean.sharpe
StdDev.annualized(portf.rebal.fm)
SortinoRatio(portf.rebal.fm)
ES(portf.rebal.fm, method = "historical")
tail(MPF.portf.weight, n = 1)


### Deflated Sharpe Ratio
SR_zero <-
  sqrt((StdDev(SR.all)) ^ 2 / 12) * ((1 - 0.57721) * qnorm(1 - 1 / 31) +
                                       (0.57721) * qnorm(1 - (1 / (31 * 2.71828))))
DSR <-
  pnorm(((portf.rebal.fm.sharpe / sqrt(12) - SR_zero) * sqrt(length(MPF.BCT.returns[, 1]))) /
          sqrt(1 - skewness(portf.rebal.fm) * portf.rebal.fm.sharpe + 
                 ((kurtosis(portf.rebal.fm) - 1) / 4) * (portf.rebal.fm.sharpe) ^ 2)
  )

rownames(DSR) <- "Deflated Sharpe Ratio"
DSR

```

### Monthly Installment
```{r linewidth=159, warning=FALSE}
MPF.BCT.units <- MPF.BCT.returns
MPF.BCT.units[, ] <- 0

MPF.monthly.asset <- MPF.BCT.returns
MPF.monthly.asset[, ] <- 0

MPF.monthly.returns <-
  as.xts(rowSums(MPF.BCT.returns), order.by = monthly)
MPF.monthly.returns[] <- 0

MPF.time <- 0:length(MPF.BCT.returns[, 1]) / 12
MPF.pay <- -1500 + 0 * MPF.time

for (row in 1:length(MPF.BCT.returns[, 1])) {
  this.price <- as.matrix(MPF.BCT[monthly[row]])
  MPF.BCT.units[row, ] <- this.price
  
  if (row == 1) {
    last.value <- 1500
    this.value <- as.numeric((1500 / MPF.BCT[1, 16]) * this.price[16])
    MPF.monthly.returns[row] <- log(this.value / last.value)
    MPF.monthly.asset[row,] <-
      (this.value + 1500) / this.price * MPF.portf.weight[row, ]
    last.price <- this.price
  } else {
    last.value <-
      as.numeric(sum(na.fill(last.price * MPF.monthly.asset[row - 1, ], 0)))
    this.value <-
      as.numeric(sum(na.fill(this.price * MPF.monthly.asset[row - 1, ], 0)))
    MPF.monthly.returns[row] <- log(this.value / last.value)
    MPF.monthly.asset[row,] <-
      (this.value + 1500) / this.price * MPF.portf.weight[row, ]
    last.price <- this.price
  }
}


total.asset.value <- sum(MPF.monthly.asset[row, ] * this.price)
total.contribution <- 1500 * length(MPF.BCT.returns[, 1])

MPF.pay[row + 1] <- total.asset.value
IRR.f <- function(r)
  sum(MPF.pay * exp(-r * MPF.time))
IRR.root <- uniroot(IRR.f, c(0, 1))


total.asset.value
total.contribution

mean.monthly.annual.return <-
  mean(do.call(rbind, lapply(split(MPF.monthly.returns, "years"), function(x)
    colMeans(x))) * 12)
mean.monthly.annual.return
IRR.root$root

stddev.monthly <- (StdDev(MPF.monthly.returns) * sqrt(12))
monthly.installment.sharpe.ratio <-
  mean.monthly.annual.return / stddev.monthly
rownames(monthly.installment.sharpe.ratio) <-
  "Sharpe Ratio (mean annual return)"
monthly.installment.sharpe.ratio
StdDev.annualized(MPF.monthly.returns)
ES(MPF.monthly.returns, method = "historical")
SortinoRatio(MPF.monthly.returns)

```
